%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Manager, Business Intelligence (Finance)} % Job title
  {HelloFresh} % Organization
  {Irving, TX} % Location
  {Jan 2024 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and implemented business intelligence strategies to optimize financial decision-making, leveraging Python, SQL, Tableau, and Streamlit to drive cost savings and efficiency.}
      \item {Designed and maintained ETL pipelines, automating data extraction, transformation, and loading (ETL) processes for seamless data integration and analysis across Finance.}
      \item {Created interactive dashboards in Tableau and Streamlit, integrating Amazon S3 for scalable data storage, real-time visualization, and enhanced user experience.}
      \item {Automated financial reporting, improving efficiency, accuracy, and scalability, streamlining workflows across Accounting, Financial Operations, HR, Procurement, and Operations to enhance collaboration and deliver more timely insights.}
      \item {Led data analysis, ad-hoc reporting, and strategic initiatives, collaborating with business stakeholders to deliver actionable insights, optimize data pipelines, and improve decision-making.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Senior Data Analyst (Finance)} % Job title
  {} % Organization
  {} % Location
  {April 2023 - January 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Utilized Python and SQL to perform advanced financial data analysis, deriving actionable insights to inform strategic decision-making.}
      \item {Developed and maintained complex financial models to support forecasting, budgeting, and long-term strategic planning across business units.}
      \item {Created interactive Tableau dashboards to visualize financial trends and KPIs, effectively communicating insights to senior management and stakeholders.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Senior Planner} % Job title
  {} % Organization
  {} % Location
  {April 2022 – April 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led end-to-end labor planning and optimization for fulfillment centers, integrating input from HR, Operations, Finance, and other departments.}
      \item {Utilized Python, Google App Script, Domo, and SQL to implement tool enhancements, automate workflows, and drive efficiency across multiple business functions.}
      \item {Managed rostering for up to 2000+ employees, forecasting labor requirements for both short-term and long-term production needs across various sites.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Planning \& Materials Associate} % Job title
  {} % Organization
  {} % Location
  {May 2021 - April 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed shift plans and managed resources across multiple fulfillment centers, ensuring alignment with production goals and SLAs.}
      \item {Collaborated with HR, Operations, Logistics, and Procurement to optimize labor and material allocation, aligning with production forecasts and weekly plans.}
      \item {Maintained and troubleshot planning tools, ensuring efficiency and data accuracy to support production teams in a high-volume environment.}
    \end{cvitems}
  }

\vspace{0.4cm}
%---------------------------------------------------------
\cventry
  {Project Manager} % Job title
  {Stonecrop Technologies} % Organization
  {Garland, TX} % Location
  {Feb. 2019 - Feb. 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led a small cell program with Nokia, managing 500 orders/month and coordinating cross-departmental efforts to meet project milestones.}
      \item {Implemented inventory management strategies across multiple facilities, achieving 99.8\% inventory accuracy and reducing shrinkage to 0.25\%.}
      \item {Managed insurance claims and scrap processes, overseeing the disposition of \$2.5M in assets and ensuring compliance with business and regulatory standards.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
    {Inventory Control Manager} % Job title
    {} % Organization
    {} % Location
    {Aug 2018 - Feb 2019} % Date
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led Inventory Control and Reverse Logistics teams, optimizing processes and ensuring inventory accuracy across multiple sites with total value up to \$900M.}
      \item {Developed reporting tools using Excel, Access, and Tableau, enabling data-driven decision-making and improving operational efficiency.}
      \item {Mentored team members and provided root cause analysis to identify areas for process improvements and reduce inventory discrepancies.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
    {Reverse Logistics Supervisor} % Job title
    {} % Organization
    {} % Location
    {Nov 2016 - Aug 2018} % Date
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and led the Reverse Logistics department, generating \$2.5M in additional revenue through the management of returns and disaggregation projects.}
      \item {Managed the Massive MIMO CDU30 Refurbishment and cabinet disaggregation projects, delivering cost savings and additional revenue streams for the company.}
      \item {Built and fostered vendor relationships, streamlining the telecommunications material scrapping process and contributing to project success.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
    {Material Follow-Up Coordinator} % Job title
    {} % Organization
    {} % Location
    {Oct 2015 - Nov 2016} % Date
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Monitored inventory accuracy for \$300M worth of materials, ensuring that all products met SLAs and resolving discrepancies in real-time.}
      \item {Led the implementation of Highjump WMS in the distribution center, optimizing material handling and improving operational efficiency.}
      \item {Provided support for Reverse Logistics, overseeing team operations to ensure materials were processed efficiently and within business requirements.}
    \end{cvitems}
  }

%---------------------------------------------------------
\end{cventries}
